Transform and Tell:\\The News Image Caption Writer That Remembers Rare Names

### 2019-11-07 paper/paper.tex
Add reference to transformer theory

%%%%%%%%% ABSTRACT
\begin{abstract}
   We propose an end-to-end model to generate image captions in news articles.
   By combining the transformer architecture, byte-pair encoding, and
   pretrained embeddings from three different modalities (RoBERTa for text,
   ResNet-152 for images, and FaceNet for faces), our system is able to
   describe an image with specific named entities mentioned in the article. Our
   model achieves a CIDEr score of 53 on the GoodNews dataset, significantly
   outperforming the previous state-of-art CIDEr of 13. We also introduce the
   NYTimes+ dataset, the largest news image captioning dataset to date.
   NYTimes+ is an extended version of GoodNews with higher-quality articles and
   metadata that allow us to study the importance of the image location within
   the text. On NYTimes+, we achieve a CIDEr of 51. Pretrained models and
   source code are available from
   \href{https://github.com}{https://anonymized}.
\end{abstract}

@@

Most existing captioning systems can only generate a generic description of an
image \cite{Vinyals2015ShowAT, Fang2015FromCT, Karpathy2015DeepVA,
Rennie2017SelfCriticalST, Lu2017KnowingWT, Anderson2017BottomUpAT}, mainly
because these architectures cannot handle an open vocabulary and early
captioning datasets such as MS COCO \cite{Lin2014MicrosoftCC,
Chen2015MicrosoftCC} and Flickr30k \cite{Young2014FromID} were annotated using
only visual cues present in the image. More recently, datasets such as TIME
\cite{Tariq2017ACE}, BreakingNews \cite{Ramisa2016BreakingNewsAA}, and GoodNews
\cite{Biten2019GoodNews} include real-life captions written by professional
journalists. To the best of our knowledge, all existing models that are trained
on these news datasets use template-based methods to insert named entities.

This motivates us to ask whether it is possible to design a fully end-to-end
model for news image captioning. The model would need to 1) attend to
contextual cues from different modalities and 2) generate captions that contain
specific information including rare proper names that have not been seen in the
training data. To answer this, we look at the recent development in
sequence-to-sequence architectures and language modeling.

The most successful family of models in natural language understanding and
generation are the transformer networks, which consist of layers of
self-attention and feed-forward connections stacked on top of each other
\cite{Vaswani2017AttentionIA}. Transformers have consistently been shown to
outperform RNN architectures in language modeling \cite{Radford2019LanguageMA},
story generation \cite{Fan2018HierarchicalNS}, summarization
\cite{Subramanian2019OnEA}, and machine translation \cite{Bojar2018Findings}.

@@

In parallel to the development of these pre-training methods, many novel
techniques have been proposed to improve training convergence and handle more
diverse data inputs. The most significant contribution is the use of byte-pair
encoding \cite{Sennrich2015NeuralMT} to handle an open vocabulary. This is done
by representing a rare word as a sequence of subword units.

@@

   \item We provide a detailed model analysis, deconstructing the most
   important modeling components and quantifying the incremental contribution
   that each of them makes not only to the popular metrics such as BLEU, ROUGE,
   METEOR, and CIDEr; but also to other linguistic measures like readability
   scores, caption length, and recall of rare names.
\end{enumerate}

>>>>

%%%%%%%%% ABSTRACT
\begin{abstract}
   We propose an end-to-end model to generate image captions in news articles.
   By combining the transformer architecture, byte-pair encoding, and
   pretrained embeddings from three different modalities (RoBERTa for text,
   ResNet-152 for images, and FaceNet for faces), our system is able to
   describe an image with specific named entities mentioned in the article. Our
   model achieves a CIDEr score of 53 on the GoodNews dataset, significantly
   outperforming the previous state-of-art CIDEr of 13. We also introduce the
   NYTimes+ dataset, the largest news image captioning dataset to date.
   NYTimes+ is an extended version of GoodNews with higher-quality articles and
   metadata that allow us to study the importance of the image location within
   the text. On NYTimes+, we achieve a CIDEr of 51. Pretrained models and
   source code are available from
   \href{https://github.com}{https://github.com/anonymized-link}.
\end{abstract}

@@

Most existing captioning systems can only generate a generic description of an
image \cite{Vinyals2015ShowAT, Fang2015FromCT, Karpathy2015DeepVA,
Rennie2017SelfCriticalST, Lu2017KnowingWT, Anderson2017BottomUpAT}, mainly
because these architectures cannot handle an open vocabulary and early
captioning datasets such as MS COCO \cite{Lin2014MicrosoftCC,
Chen2015MicrosoftCC} and Flickr30k \cite{Young2014FromID} were annotated using
only visual cues present in the image. More recently, datasets such as TIME
\cite{Tariq2017ACE}, BreakingNews \cite{Ramisa2016BreakingNewsAA}, and GoodNews
\cite{Biten2019GoodNews} include real-life captions written by professional
journalists. However, all existing models that are trained on these news
datasets use template-based methods to insert named entities.

This motivates us to ask whether it is possible to design a fully end-to-end
model for news image captioning. The model would need to 1) attend to
contextual cues from different modalities and 2) generate captions that contain
specific information including rare proper names that have not been seen in the
training data. To answer this, we look at the recent development in
sequence-to-sequence architectures and language representation learning.

The most successful family of models in the field of natural language
processing (NLP) are the transformer networks, which consist of layers of
self-attention and feed-forward connections stacked on top of each other
\cite{Vaswani2017AttentionIA}. Transformers have consistently been shown to
outperform RNN architectures in language modeling \cite{Radford2019LanguageMA},
story generation \cite{Fan2018HierarchicalNS}, summarization
\cite{Subramanian2019OnEA}, and machine translation \cite{Bojar2018Findings}.
There are theoretical justifications that transformers could be universal
approximations of sequence-to-sequence functions \cite{Anonymous2020AreTU}.

@@

In parallel to the development of these pre-training methods, many novel
techniques have been proposed to improve training convergence and handle more
diverse data inputs. The most significant contribution is the use of byte-pair
encoding (BPE) \cite{Sennrich2015NeuralMT} to represent a rare word as a
sequence of subword units, thus giving models the ability to handle an open
vocabulary.

@@

   \item We provide a detailed model analysis, deconstructing the most
   important modeling components and quantifying the incremental contribution
   that each of them makes not only to the usual metrics such as BLEU, ROUGE,
   METEOR, and CIDEr; but also to other linguistic measures like readability
   scores, caption length, and recall of rare names.
\end{enumerate}
